\section{Followup \& Notes via Emails}

\subsection{Misc}
\label{sec:Misc}
The following parts were mentioned in the meeting but not necessarily on the whiteboard, or even in the initial posting of these notes.
\begin{itemize}
  \item Joe would like to maintain a group based method to manage different responsibilities to avoid
        bottlenecks in management should someone be unavailable.
  \begin{itemize}
    \item Issues may arise with accountability when groups are not proactive in ownership of tasks.
    \item The charter\footnote{FIRST Alumni} we plan to base our own charter on provides a framework to
          easily create groups and teams as needed to work on such items.
    \item While a group may be working on a task, there is one central point of contact for such a task
          or responsibility.
    \item This allows for the essence of Joe's suggestion to enable group based allocations while
          providing a single point of accountability.\footnote{Effectively creating a driver for stuff to
          get done, whilst allowing for a team dynamic.}
  \end{itemize}
\end{itemize}

\label{sec:Followup}
\subsection{Action Items}
\begin{itemize}
  \item Pierce Rixon, David Lam and Josh Miller interested in being involved.
  \item Pierce, Tristan and possibly Adrian are not onboard with ``Knack''
  (yet), may require further discussion.
  \item Joe reports domain kcmq.com is already taken.
  \item Adam reports domain kcmq.net and kcmq.org are available.
  \item Furthermore Pierce recommends that we need to resist the urge to become
  overly ``nerdy''.
\end{itemize}

\subsection{Next Meeting}
The next meeting has been scheduled for 2012-07-13\footnote{Yes, it's Friday the
$13^\text{th}$.} in room E6A.261, or E6A.245 (conference room) should 261 be
unavailable. Time: 1530.
